An Automatic Verification Framework for Software Configurations

### 2016-05-06 OSDI/check.tex
config: checker, eval

\section{Checker}

\ennan{Here, we need to describe how we check whether 
the target configuration file meets learned rules using SMT solver.}

>>>>

\section{Checker}
\label{sec-checker}

With the learned rules and constraints in hand,
\app checks whether any entry in a target configuration file
violates the learned rules.
For a given configuration file, \app parses it using the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules to check the
following aspects of the target configuration file.

\para{Ordering violation.}
\app can check whether two or more entries have the ordering 
problem, which means whether the order of some entries in the 
target configuration follows the rules output by the learner.

\para{Correlation violation.}
\app checks if the target configuration file follows the 
correlation rules (including fine-grained value correlation rules)
learned from the training set. The rule would be ignored 
if the involved entries are absent in the target configuration file.

\para{Data type violation.}
For each entry to be checked in the target configuration file,
the checker reads its type information inferred from the training set,
and uses the generated language model to verify whether the types
are matched. A type violation is reported if the verification
fails.

\para{Suspicious warning.}
This checking occurs in the second sub-module of the checker.
Different from the previous checking tasks,
suspicious warning is just to detect whether some value
is too different (or distinguished) from the same entries in the
training dataset. Even if some values are statistically different
from the ones in the training dataset, 
it does not mean such a value is incorrect;
thus \app, in this case, throw out a warning to the user who
enters the target configuration file, and a report containing 
normal values in the training dataset.
\app allows users to choose whether they want to change 
the values according to the ones in the training configuration
files or not.

### 2016-05-06 OSDI/eval.tex
config: checker, eval

\section{Implementation and Evaluations}

\ennan{Here, we describe the implementation and evaluations}

>>>>

\section{Implementation}

\ennan{We need to describe how do we implement each module. We may need to
have three paragraphs: one is for translator, one is for learner 
and one is for checker.}

\section{Evaluations}

We mainly conduct three parts of experiments to evaluate our \app
prototype.

We want to answer several questions:

\begin{itemize}

\item Whether \app can detect real-world configuration errors?

\item How does the size of training dataset impact on the correctness
  of \app?

\item What is the rule inference accuracy?

\item How long can we run the verification?

\end{itemize}

\subsection{\app's effectiveness}

In order to evaluate the effectiveness of \app, we extract
20 misconfiguration files from a MySQL dataset~\cite{xu15hey},
and perform \app on them. \ennan{Here, we first need a table to 
list each configuration error with error type, description,
and whether \app correctly reports the issues.}

Next, we inject some errors to correct configuration files,
and run \app to check whether our framework can correctly detect
these injected errors. \ennan{We also need a table here, 
and list each injected problem.}

\subsection{Training Set Impact}

In this experiment, we vary the number of training configuration files,
and observe whether the correctness of \app would increase 
accordingly. \ennan{We may need a table whose x-axis is the number
of entries in the training configuration files, and y-axis is the 
accuracy or something close.}

\subsection{The accuracy of Rule Inference}

\ennan{I am still trying to think about this part ...}

\subsection{The Run-Time of Verification}

\ennan{Here, we need three pictures. In the first figure, x-axis should
be the number (or the size) of entries in the training dataset, and 
y-axis should be the run-time of parsing. In the second figure,
we need to measure the time of generating rules. }
